A prototype machine translation system for Kazakh and Tatar based on free/open-source components

### 2013-02-26 paper/paper.tex
add few sentences about Kazakh

The paper will be laid out as follows: Section~\ref{sec:lang}\ gives a brief description
of the two languages; Section~\ref{sec:prev}\ gives a short review of some previous
work in the area of Turkic--Turkic language translation; Section~\ref{sec:sys}\ 
describes the system and the tools used to construct it; Section~\ref{sec:eval}\ gives a very preliminary evaluation of the system; and finally Section~\ref{sec:conc}\ describes our aims for future work and some concluding remarks.

@@

Tatar is a Turkic language spoken in and around Tatarstan by approximately 6 million people.  Bashkir (Bashqort) is a Turkic language spoken by about 1.5 million people in and around Bashqortostan.  Tatarstan and Bashqortostan are both republics within Russia.  Both languages are co-official with Russian in their respective republics.  The two languages belong to the same branch of the Kypchak group of Turkic languages.  As they are very close relatives, they share many innovations, but Bashkir has quite a few phonological innovations beyond those of Tatar (such as rounding harmony and desonorisation of high-sonority suffix-initial consonants; cf.\ \citet{washington10}) and the languages have a number of morphological differences (including different volitional participles).  The spoken languages share a high level of mutual intelligibility, but many of the inherent similarities are obscured by their fairly different orthographical systems along with the phonological and morphological differences between the languages.

Aside from native speaker intuition, we also consulted the Bashkir Grammar of M. G. Usmanova \citep{usmanova06}.

>>>>

The paper will be laid out as follows: Section~\ref{sec:lang}\ gives a brief description
of the two languages; Section~\ref{sec:prev}\ gives a short review of some previous
work in the area of Turkic--Turkic language translation; Section~\ref{sec:sys}\ 
describes the system and the tools used to construct it; Section~\ref{sec:eval}\ gives
a preliminary evaluation of the system; and finally Section~\ref{sec:conc}\ describes
our aims for future work and some concluding remarks.

@@

Both languages belong to the Kypchak (or Northwestern) group of Turkic languages.
Kazakh is primarily spoken in Kazakhstan, where it is the national language. Large
groups of native speakers also exist in neigbouring Central-Eurasian republics,
China and Mongolia. Total number of speakers is at least 10 million people.
